### 2012-06-29 inst/examples/bias_table.Rmd
bias table example

`ro cache=TRUE, warning=FALSE, comment=NA, message=FALSE, cache.path="voi_sethi_parameters/", verbose=TRUE or`

@@

# Calculating the value of information

 Implements a numerical version of the SDP described in `r knitcitations::citep("10.1016/j.jeem.2004.11.005")`.
 Compute the optimal solution under different forms of uncertainty.

@@

With parameters `r` = `r r <- 1` and `K` = `r K <- 100`.

@@

``` {r miscpars}
delta <- 0.05
xT <- 0
OptTime <- 25
````

We will determine the optimal solution over a `r OptTime` time step window with boundary condition for stock at `r xT` and discounting rate of `r delta`.

# Scenarios:

We use Monte Carlo integration over the noise processes to determine the transition matrix.

``` {r beparallel, cache=FALSE}
require(snowfall)
sfInit(parallel=TRUE, cpu=16)
````

``` {r policyscenarios}
scenario <- function(policy_g, policy_m, policy_i){

  z_g <- function() 1+(2*runif(1, 0,  1)-1) * policy_g
  z_m <- function() 1+(2*runif(1, 0,  1)-1) * policy_m
  z_i <- function() 1+(2*runif(1, 0,  1)-1) * policy_i

  SDP_Mat <- SDP_by_simulation(f, pars, x_grid, h_grid, z_g, z_m, z_i, reps=2e4)
  opt <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime, xT, 
                       profit, delta, reward=0)
}
````

Determine the policies for each of the scenarios (noise combinations).

``` {r runall}
lvl <- 0.5
````

``` {r }
det <- scenario(0.0, 0.00, 0.00)
````

``` {r }
all_low <- scenario(0.1, 0.1, 0.1)
````

``` {r }
g   <- scenario(lvl, 0, 0)
````

``` {r }
m   <- scenario(0, lvl, 0)
````

``` {r }
i   <- scenario(0, 0, lvl)
````

``` {r }
gm  <- scenario(lvl, lvl, 0)
````

``` {r }
gi  <- scenario(lvl, 0, lvl)
````

``` {r }
mi  <- scenario(0, lvl, lvl)
````

``` {r }
gmi <- scenario(lvl, lvl, lvl)
````

```{r }
low <- all_low
````

@@

``` {r sethiplots}
require(reshape2)
policy <- melt(data.frame(stock = x_grid, det = det$D[,1], low=low$D[,1],
               g = g$D[,1], m = m$D[,1], i= m$D[,1], 
               gm = gm$D[,1], gi = gi$D[,1], mi = mi$D[,1], gmi = gmi$D[,1]), 
               id = "stock")

@@

value <- melt(data.frame(stock = x_grid, det=det$V, low = low$V, 
                         g = g$V, m = m$V, gm = gm$V, 
                         gi = gi$V, mi=mi$V, gmi = gmi$V), id = "stock")

@@

``` {r simfn, rerun=TRUE} 
simulatereps <- function(opt, true_g, true_m, true_i){

  z_g <- function() 1+(2*runif(1, 0,  1)-1) * true_g
  z_m <- function() 1+(2*runif(1, 0,  1)-1) * true_m
  z_i <- function() 1+(2*runif(1, 0,  1)-1) * true_i

  sims <- lapply(1:100, function(i){
    ForwardSimulate(f, pars, x_grid, h_grid, x0 = K, opt$D, z_g, z_m, z_i, profit)
  })

  sims
}
````

@@

``` {r runallsims, dependson="simfn"} 
policyfn <- list(det=det, low=low, g=g, m=m, i=i, gm=gm, gi=gi, mi=mi, gmi=gmi)
noise <- list( det  = c(0,0,0),        low = c(0.1, .1, .1),  growth = c(lvl, 0, 0),
               measure  = c(0, lvl, 0),implement = c(0,0,lvl),growth_measure = c(lvl, lvl, 0), 
               growth_implement = c(lvl, 0, lvl),  measure_implement = c(0, lvl, lvl), all = c(lvl, lvl, lvl)) 
allcases <- lapply(policyfn, function(policyfn_i){
  lapply(noise, function(noise_i){
    simulatereps(policyfn_i, noise_i[1], noise_i[2], noise_i[3])
  })
})
````

``` {r tidyall, dependson="runallsims"}
sims <- unlist(allcases, recursive=FALSE)
dat <- melt(sims, id=names(sims[[1]][[1]]))  
dt <- data.table(dat)
setnames(dt, c("L2", "L1"), c("reps", "uncertainty")) # names are nice
````

@@

``` {r  onerep, dependson="tidyall"}
ggplot(subset(dt,reps==1)) +
  geom_line(aes(time, fishstock)) +
  geom_line(aes(time, harvest), col="darkgreen") + 
  facet_wrap(~uncertainty) 
````

@@

``` {r stock, fig.cap="the induced dynamics in the stock size over time, for all replicates, by scenario", dependson="tidyall"}
p1 <- ggplot(subset(dt, fishstock>0)) 
p1 + geom_line(aes(time, fishstock, group = reps), alpha = 0.1) + facet_wrap(~uncertainty)
````

``` {r profits, fig.cap="the distribution of profits by scenario", dependson="tidyall"}
profits <-dt[ , sum(profit), by=c("reps", "uncertainty")] 
ggplot(profits) + geom_histogram(aes(V1)) + facet_wrap(~uncertainty)
````

@@

``` {r summarystats, cache=FALSE}
means <- profits[, mean(V1), by=uncertainty]
sds <- profits[, sd(V1), by=uncertainty]
````

``` {r prettytable, cache=FALSE, results="asis"}
require(xtable)
uncertainties <- names(noise) 
print(xtable(matrix(means$V1, nrow=length(noise), dimnames=list(uncertainties, uncertainties))), type="html")
print(xtable(matrix(sds$V1, nrow=length(noise), dimnames=list(uncertainties, uncertainties))), type="html")
````

>>>>

`ro cache=TRUE, warning=FALSE, comment=NA, message=FALSE, cache.path="bias_table/", verbose=TRUE or`

@@

# Calculating the bias table

@@

With `K` = `r K <- 100`, and variable choice of r.

@@

``` {r miscpars}
delta <- 0.05
xT <- 0
OptTime <- 25
sigma_g <- .5
````

We will determine the optimal solution over a `r OptTime` time step window with boundary condition for stock at `r xT` and discounting rate of `r delta`.  The Reed model considers a stochastic growth model

<div> $$ x_{t+1} = z_g f(x_t) $$ </div>

for the random variable `z_g`, given by

``` {r noise}
z_g <- function() 1+(2*runif(1, 0,  1)-1) * sigma_g
````

No other sources of noise enter into the dynamics.

``` {r othernoise}
z_m <- function() 1
z_i <- function() 1
````

## Scenario 1: low r

With parameter `r` = `r r <- 0.5`

``` {r  }
pdfn <- function(P, s){
  dunif(P, 1 - s, 1 + s)
}
SDP_Mat <- determine_SDP_matrix(f, pars, x_grid, h_grid, sigma_g, pdfn)
````

``` {r  }
opt_low <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime, xT, profit, delta, reward=0)
````

## Scenario 2: medium r

With parameter `r` = `r r <- 1`

``` {r  }
pdfn <- function(P, s){
  dunif(P, 1 - s, 1 + s)
}
SDP_Mat <- determine_SDP_matrix(f, pars, x_grid, h_grid, sigma_g, pdfn)
````

``` {r  }
opt_med <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime, xT, profit, delta, reward=0)
````

## Scenario 3: high r

With parameter `r` = `r r <- 1.5`

``` {r  }
pdfn <- function(P, s){
  dunif(P, 1 - s, 1 + s)
}
SDP_Mat <- determine_SDP_matrix(f, pars, x_grid, h_grid, sigma_g, pdfn)
````

``` {r  }
opt_high <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime, xT, profit, delta, reward=0)
````

@@

``` {r sethiplots, rerun=TRUE}
require(reshape2)
policy <- melt(data.frame(stock = x_grid, 
                          low = opt_low$D[,1],
                          med = opt_med$D[,1],
                          high = opt_high$D[,1]),
               id = "stock")

@@

value <- melt(data.frame(stock = x_grid, 
                         low=opt_low$V,
                         med=opt_med$V,
                         high=opt_high$V),
              id = "stock")

@@

``` {r simfn, rerun=TRUE} 
simulatereps <- function(opt, pars){
  sims <- lapply(1:100, function(i){
    ForwardSimulate(f, pars, x_grid, h_grid, x0 = K, opt$D, z_g, z_m, z_i, profit)
  })
  sims
}
````

@@

``` {r runallsims, dependson="simfn"} 
policyfn <- list(low=opt_low, med=opt_med, high=opt_high)
par_list <- list(c(0.5, 100), c(1, 100), c(1.5, 100))

allcases <- lapply(policyfn, function(policyfn_i){
  lapply(par_list, function(par){
    simulatereps(policyfn_i, par)
  })
})
````

``` {r tidyall, dependson="runallsims"}
sims <- unlist(allcases, recursive=FALSE)
dat <- melt(sims, id=names(sims[[1]][[1]]))  
dt <- data.table(dat)
setnames(dt, c("L2", "L1"), c("reps", "parameter")) # names are nice
````

@@

``` {r  onerep, dependson="tidyall"}
ggplot(subset(dt,reps==1)) +
  geom_line(aes(time, fishstock)) +
  geom_line(aes(time, harvest), col="darkgreen") + 
  facet_wrap(~parameter) 
````

@@

``` {r stock, fig.cap="the induced dynamics in the stock size over time, for all replicates, by scenario", dependson="tidyall"}
p1 <- ggplot(subset(dt, fishstock>0)) 
p1 + geom_line(aes(time, fishstock, group = reps), alpha = 0.1) + facet_wrap(~parameter)
````

``` {r profits, fig.cap="the distribution of profits by scenario", dependson="tidyall"}
profits <-dt[ , sum(profit), by=c("reps", "parameter")] 
ggplot(profits) + geom_histogram(aes(V1)) + facet_wrap(~parameter)
````

@@

``` {r summarystats, cache=FALSE}
means <- profits[, mean(V1), by=parameter]
sds <- profits[, sd(V1), by=parameter]
````

``` {r prettytable, cache=FALSE, results="asis"}
require(xtable)
scenarios <- names(par_list) 
print(xtable(matrix(means$V1, nrow=length(scenarios), dimnames=list(scenarios, scenarios))), type="html")
print(xtable(matrix(sds$V1, nrow=length(scenarios), dimnames=list(scenarios, scenarios))), type="html")
````
